Finding Quality Issues in SKOS Vocabularies

### 2012-06-05 analysis.tex
added WCC and cylce comments

\begin{table}[h]
\caption{Results of the quality checking functions}
\label{tab:results}

@@

\bottomrule
\end{tabular}
}
\end{center}
\end{table}

@@

% Weakly Connected Components
Three vocabularies show no weakly connected components (WCCs) because all concepts are orphan concepts and thus no relations between them are established. Two vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure. \texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional WCCs, which all contain linked authoritative and non-authoritative concepts. All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic. \texttt{Eurovoc}, for instance, contains 4 WCCs, containing 4, 5, 6 and 6775 concepts. The three smallest components contain concepts thematically related to ``Africa'', ``educational institutions'' and ``forecasts''. WCCs divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use. \texttt{GTAA} consists of 621 WCCs with the largest one being a subject thesaurus containing 8413 concepts. Most of the other components contain less than 10 concepts, representing, e.g., locations, person names, and genres. \texttt{PXV} splits into 10 topic-related WCCs, such as ``deficiencies'', ``defects'' or ``signals''. The \texttt{LVAk} thesaurus contains 11 concept clusters, some of them are obviously forgotten test data.

% Cyclic Hierarchical Relations
Hierarchical cycles are not a common issue except in the collaboratively created \texttt{DBpedia} vocabulary, where many concepts have reflexive \texttt{skos:broader} relations.
% Valuless Associative Relations
Valueless associative relations occur in 8 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies.
% Solely Transitive Related Concepts
Solely transitive related concepts occur in 3 vocabularies, establishing relations using properties that, according to the SKOS reference documentation, should not be asserted directly. This indicates a possible misinterpretation of the SKOS specification and could result in a loss in recall on hierarchical queries.
% Omitted Top Concepts
\texttt{GTAA} and \texttt{Geonames} omit top concepts in all concept schemes they define. \texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply contains all concepts defined in the vocabulary. Such an ``umbrella concept scheme'' without top concept is also present in \texttt{LCSH} and \texttt{NYTP}.
% Top Concepts Having Broader Concepts
Only the \texttt{PXV} vocabulary is affected by top concepts having broader concepts in its current version. In earlier versions more of them could be found which were, according to the vocabulary creator, abandoned but still available in the triple store, probably caused by some bug in the vocabulary management software.

>>>>

\vspace{-.3cm}
\begin{table}[h]
\caption{Results of the quality checking functions}
\vspace{-.3cm}
\label{tab:results}

@@

\bottomrule
\end{tabular}
}
\end{center}
\end{table}
\vspace{-.5cm}

@@

% Weakly Connected Components
Three vocabularies show no weakly connected components (WCCs) because all concepts are orphan concepts and thus no relations between them are established. Two vocabularies (\texttt{IPSV}, \texttt{NAICS}) consist of only one ``giant component'', which is often considered as being the ideal vocabulary structure. \texttt{STW} forms one giant component (containing 24,572 concepts), but has also 140 additional WCCs, which all contain linked authoritative and non-authoritative concepts. All other vocabularies split into several clusters of semantically related concepts, each of which represents a certain subtopic. \texttt{Eurovoc}, for instance, contains 4 WCCs, containing 4, 5, 6 and 6775 concepts. 
It is organized into numerous micro-thesauri and domains, using a custom ontology. Concepts contained in different micro-thesauri or domains are connected by \texttt{skos:related} properties, but this is not the case for the three small WCCs, indicating a quality flaw. WCCs divide the \texttt{Meketre} vocabulary into different topics, e.g., museums or concepts reserved for internal use. \texttt{GTAA} consists of 621 WCCs with the largest one being a subject thesaurus containing 8413 concepts. Most of the other components contain less than 10 concepts, representing, e.g., locations, person names, and genres. \texttt{PXV} splits into 10 topic-related WCCs, such as ``deficiencies'', ``defects'' or ``signals''. The \texttt{LVAk} thesaurus contains 11 concept clusters, some of them are obviously forgotten test data.

% Cyclic Hierarchical Relations
Hierarchical cycles are not a common issue except in the collaboratively created \texttt{DBpedia} vocabulary, where many concepts have reflexive \texttt{skos:broader} relations. Also some of the cycles in \texttt{MeSH} indicate badly-defined relations and those in \texttt{LVAk} may be revised regarding hierarchy changes or replacement by associative relations or synonym definitions.
% Valuless Associative Relations
Valueless associative relations occur in 8 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies.
% Solely Transitive Related Concepts
Solely transitive related concepts occur in 3 vocabularies, establishing relations using properties that, according to the SKOS reference documentation, should not be asserted directly. This indicates a possible misinterpretation of the SKOS specification and could result in a loss in recall on hierarchical queries.
% Omitted Top Concepts
\texttt{GTAA} and \texttt{Geonames} omit top concepts in all concept schemes they define. \texttt{Eurovoc} uses 128 concept schemes but has one without top concept, which simply contains all concepts defined in the vocabulary. Such an ``umbrella concept scheme'' without top concept is also present in \texttt{LCSH} and \texttt{NYTP}.
% Top Concepts Having Broader Concepts
Only the \texttt{PXV} vocabulary is affected by top concepts having broader concepts in its current version. In earlier versions more of them could be found which were, according to the vocabulary creator, abandoned but still available in the triple store, probably caused by some bug in the vocabulary management software.

### 2012-06-05 conclusions.tex
added WCC and cylce comments

In this paper we presented possible quality issues in SKOS vocabularies and described how we implemented them as quality checking functions in our qSKOS quality assessment tool. We analyzed a representative set of existing SKOS vocabularies and found  issues in all of them. Labeling and documentation issues were omnipresent and also structural issues, which require further investigation by the vocabulary maintainers, were found in most vocabularies. Although SKOS is designed for Linked Data, many existing vocabularies still resemble their closed-system origin, which results in a relatively low number of in- and out-links. Broken links are a major issue and call for synchronization mechanisms in order to maintain navigability between concepts in different vocabularies.

>>>>

We presented possible quality issues in SKOS vocabularies and described how we implemented them as quality checking functions in our qSKOS quality assessment tool. We analyzed a representative set of existing SKOS vocabularies and found  issues in all of them. Labeling and documentation issues were omnipresent and also structural issues, which require further investigation by the vocabulary maintainers, were found in most vocabularies. Although SKOS is designed for Linked Data, many existing vocabularies still resemble their closed-system origin, which results in a relatively low number of in- and out-links. Broken links are a major issue and call for synchronization mechanisms in order to maintain navigability between concepts in different vocabularies.
